Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-12-18 related.tex
Update related work.

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
dynamic information flow tracking\cite{testudo-micro08}.
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, which is one of the target applications of our architecture.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring to meet deadlines for hard real-time systems.

In contrast, our work is the first that we know of to present a general hardware platform that enables
partial monitoring. The architecture is designed to be applicable to a wide range of monitoring
techniques as well as monitor implementations (core, FPGA, etc.). By studying various potential
uses of partial monitoring, including sampling for cooperative debugging and
partial protection for low overheads, we also identified important trade-offs in dropping
policy decisions to consider in order to best meet the requirements of the
application.

>>>>

% Previous work on sampling for monitoring
\begin{table}[t]
  \begin{center}
    \vspace{-0.0in}
    \begin{footnotesize}
    \input{tabs/previous_sampling}
    \end{footnotesize}
    \caption{Previous work on partial run-time monitoring.}
    \vspace{-0.2in}
    \label{tab:monitoring.previous_sampling}
  \end{center}
\end{table}

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overheads. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overheads but does not try
  to bound overheads, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, almost all previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

For example, there exists previous work for using statistical sampling to
reduce the performance overheads of various debugging techniques. These include
sampling for bug isolation \cite{liblit-pldi05}, memory leak detection
\cite{chilimbi-asplos04}, race detection \cite{literace-pldi09, pacer-pldi10},
and information flow tracking \cite{testudo-micro08, greathouse-cgo11}. These
techniques modify the monitoring to support statistical sampling and so are not
generalizable. For those that prevent false positives, this is also done with
monitor-specific modifications. Finally, with the exception of the work by
Greathouse et al. \cite{greathouse-cgo11}, they do not allow an overhead target
to be specified.

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overheads
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overheads. QVM does prevents false positives
but does so be enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.

% In contrast, our work is the first that we know of to present a general hardware platform that enables
% partial monitoring. The architecture is designed to be applicable to a wide range of monitoring
% techniques as well as monitor implementations (core, FPGA, etc.). By studying various potential
% uses of partial monitoring, including sampling for cooperative debugging and
% partial protection for low overheads, we also identified important trade-offs in dropping
% policy decisions to consider in order to best meet the requirements of the
% application.

% % Sampling
% Statistical sampling is a method that has been applied to various debugging
% techniques in order to reduce their performance overheads. For example, Liblit
% et al. sampled program runs of thousands of users in order to find bugs
% \cite{liblit-pldi05}. This idea has also been applied to detecting memory
% leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
% dynamic information flow tracking~\cite{testudo-micro08}.
% These sampling-based techniques all limit the debugging capabilities in order
% to provide lower performance overheads, which is one of the target applications of our architecture.
% % Limited Monitoring
% In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
% modification of the Java Virtual Machine (JVM) that supports run-time
% monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
% al. created a framework for controlling the overheads of software-based
% monitoring \cite{huang-sttt12}. 
% Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
% monitoring to meet deadlines for hard real-time systems.
